---
title: "Our Regression Analysis"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r load-packages, include=FALSE}
library(tidyverse)
library(leaps)
library(lubridate)
library(broom)
```
```{r load-data, include=FALSE}
video_game_sales <- read.csv("data/Video_Games_Sales_as_at_22_Dec_2016.csv")
```
```{r regressiondata, include=FALSE}
regressiondata <- video_game_sales %>% 
  filter(Genre %in% c("Sports", "Action", "Misc", "Shooter", "Simulation") & 
                        Publisher %in% c("Electronic Arts", 
                                         "Activision", 
                                         "Namco Bandai Games",
                                         "Ubisoft",
                                         "Konami Digital Entertainment") &
           Rating %in% c("E", "E10+", "M", "T")) %>% 
  mutate(Year_of_Release = as.numeric(Year_of_Release)) %>% 
  select(Genre, Publisher, Global_Sales, Rating, Year_of_Release)
  
 

regressiondata
```
**Goal** :
To create a regression equation to predict `Global Sales` by `Publisher`, `Genre`, `Rating`, and `Year of Release`.

To accomplish our goal, first we decided to trim `Publisher` and `Genre` down to the top five in each category. We did this because of the large number of Publishers and Genres. We also trimmed `Rating` down to be either E, E10+, M or T for the same reasoning. The possible values for each variable are listed below.

- `Publisher` : Electronic Arts, Activision, Namco Bandai Games, Ubisoft, Konami Digital Entertainment
- `Genre` : Sports, Action, Misc, Shooter, Simulation
- `Rating` : E, E10+, M, T

**Model Selection** :
We decided to use backwards model selection for our analysis. In other words, we started with all four explanatory variables in our model, and removed insignificant variables at the `alpha = 0.05` level. `Year of Release` was the only variable found to be insignificant with a p-value of `0.0664`. The other variables had at least one category with a significant p-value and were kept in the model.

**Final Model** : 
Global Sales = Genre + Publisher + Rating

```{r regressionmodel, echo=FALSE}
Model <- lm(log(Global_Sales) ~ Genre + Publisher + Rating + Year_of_Release, data = regressiondata)

summary(Model)
Model %>% 
  glance() %>% 
  select(r.squared)
```
**Conclusions** :
While our variables in our model were significant, an adjusted r-squared value of `0.0735` is not good. This tells us our model only explains `7.35%` of the variation in `Global Sales`. While this is not surprising considering there are many potential factors which affect `Global Sales`; our model cannot reliably predict `Global Sales`.




















