---
title: "Final Report"
author: "S01-Blue"
output: 
  html_document:
      keep_md: yes
      toc: true
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r load-packages, include=FALSE}
library(tidyverse)
library(leaps)
library(lubridate)
```
```{r load-data, include=FALSE}
video_game_sales <- read.csv("data/Video_Games_Sales_as_at_22_Dec_2016.csv")
release_dates <- read.csv("data/query (1).csv")
```
## Introduction

### Our Dataset

For our final project we decided to work with a dataset found on [Kaggle](https://www.kaggle.com/). This dataset is a list of all video game sales as of December 22, 2016. Our dataset contained the following variables:

- Name : Name of the video game
- Platform : Platform the game was released on
- Year_of_Release : Year the game was released
- Genre : Genre of the video game
- Publisher : Publisher of the video game
- NA_Sales : North American Sales (Millions USD)
- EU_Sales : European Sales (Millions USD)
- JP_Sales : Sales in Japan (Millions USD)
- Other_Sales : Sales in other countries (Millions USD)
- Global_Sales : Global Sales (USD)
- Critic_Score : Average critic score out of 100
- Critic_Count : Number of critic reviews
- User_Score : Average user score out of 10
- User_Count : Number of user reviews
- Developer : Developer of the video game
- Rating : The video games censorship rating

### General Research Questions and Ideas

Using an exploratory data analysis for [application 05](https://github.com/sta518/application05-s01-blue) we developed some ideas and questions on how we would like to analyze this dataset. The ideas were as follows:

1. Could we create a regression to predict global sales using this dataset?
2. Create an RShiny application containing a table with this dataset where you can search the global sales for any video game in the dataset.
3. Create visualizations to show the average global sales by month of release and average global sales by year of release. Are there any trends or abnormalties?

## Data Analysis Plan





